---
title: "Data processing for Yann Bozec"
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    number_sections: false
---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
library(ggplot2)
library(seacarb) 
library(reshape2)
library(plyr)
library(tidyr)
library("lmodel2") # model II regression
library("dplyr", warn.conflicts = FALSE)
library(lubridate)
library(knitr)
#opts_knit$set(root.dir = '../')
library(scales)
library(dygraphs)
library(xts)
#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp166_seafet/1b_seafet_pointB/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp166_seafet/1b_seafet_pointB/"

```

# Introduction
This document and data file were generated for Yann Bozec (yann.bozec@sb-roscoff.fr). The request was to use our high frequency pH (seaFET) data at Point B and compare them with pCO2 data from the Channel. Here we calculate pCO2, using high frequency measurements of pH and temperature and discrete measurements (SOMLIT) of salinity, total alkalinity and nutrients.

# Information on data 

### Nutrients
Last silicate (Si_ptb) and phosphate (P04_ptb) data available: 2018-05-02. More recent samples have not been analysed yet.

### Total alkalinity
Last alkalinity data (at_ptb) available: 2018-06-04. Recent samples have not been analysed yet.

### Salinity
The salinity is up to date. 

### pH seaFET
Last pH data available: 2018-04-21. After this date, the instrument was sent to seabird for maintenance.

pH data (pHT_ sfint) have been calibrated against reference samples measured with the spectrophotometric method.

### *p*CO~2~
*p*CO~2~ has been calculated with the carb function of the seacarb R package (3.2.8). Salinity, total alkalinity, silicate and phosphate concentrations are from weekly Point B sampling. Default constants were used.  These unique weekly data, mostly sampled on tuesdays, have been spread around the sampling date until the middle time which separate them from the next weekly sampling.

# Conclusion
Data file is data_bozec.csv. 

```{r read data, include=FALSE}

all <- read.table(paste0(path, "./pb_data/all_data/continuous_discrete.csv"), header=T, sep=",", dec=".", as.is=T)
all$date <- ymd_hms(all$date)
all <- all%>%
  dplyr::filter(date <= "2018-04-22")%>%
  dplyr::select(date, T_seaF, pHT_sfint, S_ptb, at_ptb, PO4_ptb, Si_ptb)

carb <- carb(8, all$pHT_sfint, all$at_ptb*0.000001, S=all$S_ptb, T=all$T_seaF, P=0, Pt=all$PO4_ptb*1e-6, Sit=all$Si_ptb*1e-6 ,k1k2="x", kf="x", ks="d", pHscale="T", b="l10")
all$pCO2_calc<- carb$pCO2

write.table(all,paste0(path,"pb_output/data_bozec.csv"),row.names = FALSE, sep=",", dec=".")

```

# Plots
```{r plots, echo=FALSE, warning=FALSE, message=FALSE}
# pH seaFET
pH_xts <- dplyr::select(all,date, pHT_sfint)
pH_xts <- as.xts(pH_xts, order.by=pH_xts$date)
dygraph(pH_xts, main="pH calibrated", ylab="pH in total scale") %>%
  dySeries("pHT_sfint", color = "blue", strokeWidth = 0, label = "pH") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# pCO2
pco2_xts <- dplyr::select(all,date, pCO2_calc)
pco2_xts <- as.xts(pco2_xts, order.by=pco2_xts$date)
dygraph(pco2_xts, main="Calculated pCO2", ylab="Calculated pCO2 in μatm") %>%
  dySeries("pCO2_calc", color = "blue", strokeWidth = 0, label = "Calculated pCO2") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# TA
ta_xts <- dplyr::select(all,date, at_ptb)
ta_xts <- as.xts(ta_xts, order.by=ta_xts$date)
dygraph(ta_xts, main="Total alkalinity", ylab="Total alkalinity in µmoles/kg") %>%
  dySeries("at_ptb", color = "blue", strokeWidth = 0, label = "pH") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# Temp
temp_xts <- dplyr::select(all,date, T_seaF)
temp_xts <- as.xts(temp_xts, order.by=temp_xts$date)
dygraph(temp_xts, main="Temperature", ylab="Temperature in °C") %>%
  dySeries("T_seaF", color = "blue", strokeWidth = 0, label = "seaFET Temperature") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# Sal
sal_xts <- dplyr::select(all,date, S_ptb)
sal_xts <- as.xts(sal_xts, order.by=sal_xts$date)
dygraph(sal_xts, main="Salinity", ylab="Salinity in psu") %>%
  dySeries("S_ptb", color = "blue", strokeWidth = 0, label = "Salinity") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# Nutrients
nut_xts <- dplyr::select(all,date, PO4_ptb, Si_ptb)
nut_xts <- as.xts(nut_xts, order.by=nut_xts$date)
dygraph(nut_xts, main="Nutrients", ylab="Nutrients in mol/kg") %>%
  dySeries("PO4_ptb", color = "blue", strokeWidth = 0, label = "Phosphate") %>%
   dySeries("Si_ptb", color = "green", strokeWidth = 0, label = "Silicate") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)

```

#Acknowlegments

**The sailors:** J.-Y Carval, J.-L Prevost, P. Cohen. 

**Point B team:** L. Mousseau, F. Petit, O. Passafiume, M. Durozier, A.-M. Corre, H. De Lary. 

**EOL buoy engineer:** J.-M Grisoni.

**Divers:** G. De Liège and D. Luquet
