---
title: "Yann_Bozec_collaboration"
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false
---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
library(ggplot2)
library(seacarb) 
library(reshape2)
library(plyr)
library(tidyr)
library("lmodel2") # model II regression
library("dplyr", warn.conflicts = FALSE)
library(lubridate)
library(knitr)
#opts_knit$set(root.dir = '../')
library(scales)
library(dygraphs)
library(xts)
#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp166_seafet/1b_seafet_pointB/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp166_seafet/1b_seafet_pointB/"

```

#{.tabset .tabset-fade .tabset-pills}


## Introduction
This document was done following the email sent by Yann Bozec (yann.bozec@sb-roscoff.fr) to Frederic Gazeau on 12 November 2018. The request is to use our high frequency pH (seaFET) data at Point B and compare them with pCO2 data from Occidental Manche. The principle will be to convert pH to pCO2, thanks to seacarb package and discrete data (salinity, alkalinity and nutrients).

## Data informations

### Nutrients
Last nutrients data, silicate (Si_ptb) and phosphate (P04_ptb), available: 2018-05-02. Recent samples have not been analysed yet.

### Total alkalinity
Last alkalinity data (at_ptb) available: 2018-06-04. Recent samples have not been analysed yet.

### Salinity
The salinity is up to date. 

### pH seaFET
Last pH data available: 2018-04-21. After this date, sensor was sent to calibration/fixing.
pH data (pHT_ sfint) have been calibrated against reference samples measured with the spectrophotometric method.

### *p*CO~2~
*p*CO~2~ have been calculated with the function "carb" in "seacarb" package (R project). Salinity, total alkalinity, silicate and phosphate concentrations from weekly Point B sampling have been put as inputs for the function. 
These unique weekly data, mostly sampled on tuesdays, have been spread around the sampling date until the middle time which separate them from the next weekly sampling. 

### Conclusion
According to the following points, we will give an entire dataset until last seaFET pH measurement on the 2018-04-21. Data file is data_bozec.csv. 




```{r read data, include=FALSE}

all <- read.table(paste0(path, "./pb_data/all_data/continuous_discrete.csv"), header=T, sep=",", dec=".", as.is=T)
all$date <- ymd_hms(all$date)
all <- all%>%
  dplyr::filter(date <= "2018-04-22")%>%
  dplyr::select(date, T_seaF, pHT_sfint, S_ptb, at_ptb, PO4_ptb, Si_ptb)

carb <- carb(8, all$pHT_sfint, all$at_ptb*0.000001, S=all$S_ptb, T=all$T_seaF, P=0, Pt=all$PO4_ptb*1e-6, Sit=all$Si_ptb*1e-6 ,k1k2="x", kf="x", ks="d", pHscale="T", b="l10")
all$pCO2_calc<- carb$pCO2

write.table(all,paste0(path,"pb_output/data_bozec.csv"),row.names = FALSE, sep=",", dec=".")

```

## Plots
```{r plots, echo=FALSE, warning=FALSE, message=FALSE}
# pH seaFET
pH_xts <- dplyr::select(all,date, pHT_sfint)
pH_xts <- as.xts(pH_xts, order.by=pH_xts$date)
dygraph(pH_xts, main="pH calibrated", ylab="pH in total scale") %>%
  dySeries("pHT_sfint", color = "blue", strokeWidth = 0, label = "pH") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# pCO2
pco2_xts <- dplyr::select(all,date, pCO2_calc)
pco2_xts <- as.xts(pco2_xts, order.by=pco2_xts$date)
dygraph(pco2_xts, main="Calculated pCO2", ylab="Calculated pCO2 in μatm") %>%
  dySeries("pCO2_calc", color = "blue", strokeWidth = 0, label = "Calculated pCO2") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# TA
ta_xts <- dplyr::select(all,date, at_ptb)
ta_xts <- as.xts(ta_xts, order.by=ta_xts$date)
dygraph(ta_xts, main="Total alkalinity", ylab="Total alkalinity in µmoles/kg") %>%
  dySeries("at_ptb", color = "blue", strokeWidth = 0, label = "pH") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# Temp
temp_xts <- dplyr::select(all,date, T_seaF)
temp_xts <- as.xts(temp_xts, order.by=temp_xts$date)
dygraph(temp_xts, main="Temperature", ylab="Temperature in °C") %>%
  dySeries("T_seaF", color = "blue", strokeWidth = 0, label = "seaFET Temperature") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# Sal
sal_xts <- dplyr::select(all,date, S_ptb)
sal_xts <- as.xts(sal_xts, order.by=sal_xts$date)
dygraph(sal_xts, main="Salinity", ylab="Salinity in psu") %>%
  dySeries("S_ptb", color = "blue", strokeWidth = 0, label = "Salinity") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# Nutrients
nut_xts <- dplyr::select(all,date, PO4_ptb, Si_ptb)
nut_xts <- as.xts(nut_xts, order.by=nut_xts$date)
dygraph(nut_xts, main="Nutrients", ylab="Nutrients in mol/kg") %>%
  dySeries("PO4_ptb", color = "blue", strokeWidth = 0, label = "Phosphate") %>%
   dySeries("Si_ptb", color = "green", strokeWidth = 0, label = "Silicate") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)

```

##Acknowlegments

**The sailors:** J.-Y Carval, J.-L Prevost, P. Cohen. 

**Point B team:** L. Mousseau, F. Petit, O. Passafiume, M. Durozier, A.-M. Corre, H. De Lary. 

**EOL buoy engineer:** J.-M Grisoni.

**Divers:** G. De Liège, D. Luquet, S. Alliouane
