---
title: "Data processing for Sam Dupont"
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    number_sections: false
---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
library(ggplot2)
library(seacarb) 
library(reshape2)
library(plyr)
library(tidyr)
library("lmodel2") # model II regression
library("dplyr", warn.conflicts = FALSE)
library(lubridate)
library(knitr)
#opts_knit$set(root.dir = '../')
library(scales)
library(dygraphs)
library(xts)
#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp166_seafet/1b_seafet_pointB/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp166_seafet/1b_seafet_pointB/"

```

# Introduction
This document and data file were generated for Sam Dupont (sam.dupont@bioenv.gu.se). The request was to use our high frequency pH (seaFET) data at Point B to design an experiment.

# Information on data 

### pH seaFET
Last pH data available: 2019-03-27. Hourly pH data at in situ temperature (pHT_ sfint) have been calibrated against reference samples measured with the spectrophotometric method.

# Conclusion
Data file is data_dupont.csv. 

```{r read data, include=FALSE}

all <- read.table(paste0(path, "./pb_data/all_data/continuous_discrete.csv"), header=T, sep=",", dec=".", as.is=T)
all$date <- ymd_hms(all$date)
all <- all%>%
  #dplyr::filter(date <= "2018-04-22")%>%
  dplyr::select(date, T_seaF, pHT_sfint)

#carb <- carb(8, all$pHT_sfint, all$at_ptb*0.000001, S=all$S_ptb, T=all$T_seaF, P=0, Pt=all$PO4_ptb*1e-6, Sit=all$Si_ptb*1e-6 ,k1k2="x", kf="x", ks="d", pHscale="T", b="l10")
#all$pCO2_calc<- carb$pCO2

write.table(all, paste0(path,"pb_output/data_dupont.csv"),row.names = FALSE, sep=",", dec=".")

```

# Plots
```{r plots, echo=FALSE, warning=FALSE, message=FALSE}
# pH seaFET
pH_xts <- dplyr::select(all,date, pHT_sfint)
pH_xts <- as.xts(pH_xts, order.by=pH_xts$date)
dygraph(pH_xts, main="pH calibrated", ylab="pH in total scale") %>%
  dySeries("pHT_sfint", color = "blue", strokeWidth = 0, label = "pH") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)

# Temp
temp_xts <- dplyr::select(all,date, T_seaF)
temp_xts <- as.xts(temp_xts, order.by=temp_xts$date)
dygraph(temp_xts, main="Temperature", ylab="Temperature in °C") %>%
  dySeries("T_seaF", color = "blue", strokeWidth = 0, label = "seaFET Temperature") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)


```

#Acknowledgments

**The sailors:** J.-Y Carval, J.-L Prevost, P. Cohen. 

**Point B team:** L. Mousseau, F. Petit, O. Passafiume, M. Durozier, A.-M. Corre, H. De Lary. 

**EOL buoy engineer:** J.-M Grisoni.

**Divers:** G. De Liège and D. Luquet
